\documentclass[12pt,letterpaper]{article}

\setlength{\headheight}{15pt}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{mathptmx}
\usepackage{csquotes}



\graphicspath{{/figures}}
\setlength{\parindent}{0pt}
\usepackage{ragged2e}
\usepackage{setspace}
\onehalfspacing
\justifying
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\fancyfoot[C]{\thepage}
\begin{document}
\begin{center}\section*{Project Proposal}
    \vspace{-1em}
\subsubsection*{COMP 579 - Final Project}


\end{center}

\subsubsection*{Project Information}

Proposed Title: Upgrading late exploitation in PPO with Replay Buffers, LSTMs, and Parameter Decay

<<<<<<< HEAD
Authors: Eric Sun (), Sumukh Patel (261276753), Adrien Bélanger (261118168)
=======
Authors: Eric Sun (261103545), Sumukh Patel (), Adrien Bélanger (261118168)
>>>>>>> refs/remotes/origin/main

\subsubsection*{Background \& Motivation}
Paper \cite{PPOPaper}
% --------- Work in progress ---------
Proximal Policy Optimization algorithms, which were introduced by Schulman et al. from OpenAI in 2017, are a mainstream approach for policy improvement. \cite{PPOPaper}
They are appreciated for their speed, efficiency and simplicity \cite{PPOPaper}. 
However, when compared to other algorithms, it fails to fully exploit in the last episodes, 
a flaw that is illustrated in table 2 of the Atari Benchmark of the original paper, where it fails
to beat the \textit{Actor Critic with Experience Replay} agent. \cite{PPOPaper,ACERPaper} \ This project aims to remedy this lapse in performance by implementing the following three approaches (both simultaneously and on their own): decaying clipping and learning rate parameters, adding a replay buffer, switching the MLP framework used in the paper for an LSTM-based approach for better capturing long term dependencies.
This is particularly interesting because PPO is a popular approach for the problem, and any sizable improvement could mean a significant boost in a multitude of problems that use PPOs, such as in RLHF language models and complex video game benchmarks. \cite{RLHF,dota}
% \--------- Work in progress ---------
\subsubsection*{Methods}

% Note: One thing I didn't get to in the background and motivation was the fact that these approaches might hurt PPO's efficiency and speed, which might ruin the point. 
% We should maybe do an analysis of the efficiency before and after our approaches? - Adrien


We implement Proximal Policy Optimization (PPO) following \cite{PPOPaper} and evaluate it on a subset of Atari 2600 games from the Arcade Learning Environment, focusing on environments where PPO underperforms in final performance (e.g., ChopperCommand, FishingDerby, Centipede, Breakout, MsPacman). As baselines, we use the standard PPO implementation and reported results from ACER \cite{ACERPaper}. We study three modifications aimed at improving late-stage performance: (1) annealing the clipping parameter and learning rate, (2) augmenting PPO with a replay buffer, and (3) replacing the MLP policy/value networks with an LSTM-based architecture. Each variant is evaluated independently and in combination, using the average episodic reward over the last 100 episodes as the primary metric, alongside learning curves over training frames. This experimental design enables controlled ablations while maintaining feasible computational cost. We will also review other papers with different approaches to a similar task. \cite{recurrmodel,andry}


% -------------------------
\vfill \newpage
\bibliographystyle{ieeetr}
\bibliography{bibliography}





\end{document}
